Local Group Satellite Distributions in the Illustris Simulation

### 2017-10-06 paper/paper.tex
+1 paragraph on LG width

>>>>

The upper right panel shows two interesting things. 
First, the MW satellite plane is thiner than its M31
counterpart. 
This is in principle unexepected since M31 is more
massive than the MW and it should have a broader satellite
distribution. 
The second interesting point is that the MW satellite plane is also
thiner than the spherical randomized expectation, while the M31 plane
is right within the expectation of the randomized satellites. 
This is a another piece of evidence showing the highly structured
satellite distribution in the MW in comparison to M31. 
The fact that the \rand\ samples also show a trend towards thinner MW
planes means that the radial satellite distribution in concentrated in
the MW than it is in M31.

The lower two panels re-inforce the picture of a highly structured.
